### 2013-07-24 doc/asplos14/evaluation.tex
oops fixed some Grappas

Since \Grappa's tasks are implemented entirely in software, it is easy
to support arbitrary synchronization semantics. \Grappa allows both
XMT-like per-vertex task joins as well as whole-problem joins that are
a better fit for UTS\@. \Grappa's work-stealing distributed
task queue encourages locality in task
execution so that the system is optimized for the common case of a
processor executing a task it spawned. Furthermore, Grappa's parallel
loop granularity and buffering features provide a disciplined way for the programmer to easily take better
advantage of spatial locality when it oviously exists,
specifically when reading a vertex's edgelist.
>>>>>>> better description of Grappa advantages in UTS over XMT

>>>>

Since \Grappa's tasks are implemented entirely in software, it is easy
to support arbitrary synchronization semantics. \Grappa allows both
XMT-like per-vertex task joins as well as whole-problem joins that are
a better fit for UTS\@. \Grappa's work-stealing distributed
task queue encourages locality in task
execution so that the system is optimized for the common case of a
processor executing a task it spawned. Furthermore, \Grappa's parallel
loop granularity and buffering features provide a disciplined way for the programmer to easily take better
advantage of spatial locality when it oviously exists,
specifically when reading a vertex's edgelist.
